---
title: "A3_Duong_Tram"
author: "TramooD17"
date: "25/01/2022"
output: html_document
---
## Project Info
Date: 2022 January 25  
GitHub Repository Link: https://github.com/TramooD17/Assignment-3  
Username: TramooD17  
Student #: 20109161  
17CTTD

## Assignment
Loading data and packages:
```{r}
library("dplyr")
library("tidyverse")
```
```{r}
MyDat=read.csv("./InputData/FallopiaData.csv")
```
The following code will:

Remove rows with ‘Total’ biomass < 60;

Reorder the columns so that they are in the order: ‘Total’, ‘Taxon’, ‘Scenario’, ‘Nutrients’, and remove the other columns;

Make a new column TotalG, which converts the ‘Total’ column from mg to grams AND replace Total with TotalG, and add it to the dataset.
```{r}
Dat2 <- MyDat %>%
  filter(Total<60) %>%
  select(Total, Taxon, Scenario, Nutrients) %>%
  mutate(TotalG = Total/100)%>%
  select(TotalG, Taxon, Scenario, Nutrients, -Total)
```
The following is a custom function that will take two inputs from the user:

1. a vector of data to process (e.g. column from a data.frame object) and

2. a string that defines what calculation to perform.
- if string #2 is "Average" then calculate the average value for the column named in vector #1
- if string #2 is "Sum" then calculate the sum of values for the column named in vector #1
- if string #2 is "Observations" then count the number of observed values for the column named in vector #1
- if string #2 is anything else, then output an error to the user
```{r}
Func1 <- function(vec1 = 0, string2 = 0){
  if (string2 == "Average") {
    cat("\nAverage\n")
    return(mean(vec1))
  }
  if (string2 == "Sum"){
    cat("\nSum\n")
    return(sum(vec1))
  }
  if (string2 == "Observations"){
    cat("\nObservations\n")
    return(length(vec1))
  }
 if (string2 != "Average") {
   print("Error")
 }
  if (string2 != "Sum") {
    print("Error")
  }
  if (string2 != "Observations") {
    print("Error")
  }
}
```
Write some R code that uses your function to count the total number of observations in the 'Taxon' column.
```{r}
Func1(MyDat$Taxon, "Observations")
```
Write some R code that uses your function to calculate the average TotalG for each of the two Nutrient concentrations.
```{r}
averages <- Dat2 %>%
  group_by(Nutrients) %>%
summarise(Average = Func1(vec1 = TotalG, string2 = "Average"))

print(averages)
```
Write (i.e. save) the new data to a file called "WrangledData.csv" in the Output folder.
```{r}
write.csv(averages, "./Output/WrangledData.csv")
```

