---
title: "Regex"
author: "TramooD17"
date: "01/02/2022"
output: html_document
---
 Name: Tram Duong  
 SN: 20109161  
 GitHub: TramooD17  
 
 ## Part 1: Data Science  
Import measurements.csv file from into an object called MData
```{r}
MData <- read.csv("measurements.csv")
head(MData)
```
Opening dplyr:
```{r}
library("dplyr")
```

Use a dplyr command AND regular expression(s) to add a new column called Sp that shortens the genus name in the Organism column to only the first letter and period. For example: Homo sapiens in the original Organism column becomes H. sapiens in the Sp column. 
```{r}
MData <- mutate(MData, Sp = sub("(\\w)\\w+","\\1.", Organism))
head(MData)
```
Use a dplyr command to create a new dataset BUT with Sp column instead of the Organism column, moved to the beginning in place of the original Organism column.
```{r}
MData2 <- select(MData, Sp, Limb.width, Limb.length, Observer)
```
Save the dataset as a new file called MeasShort.csv.
```{r}
write.csv(MData2, "MeasShort.csv")
```

